### 2024-03-04 ms.qmd
Updates

```{r, resultsRev}
# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
## 1) L. delicata
deli_CORTCold <- deli$b_trial_reversal
deli_ControlCold <- (deli$'b_trial_reversal:cortControl' + deli$b_trial_reversal)
deli_CORTHot <- (deli$'b_trial_reversal:tempHot' + deli$b_trial_reversal)
deli_ControlHot <- (deli$'b_trial_reversal:cortControl:tempHot' + deli$b_trial_reversal + deli$'b_trial_reversal:cortControl' + deli$'b_trial_reversal:tempHot')
## 2) L. guichenoti
guich_CORTCold <- guich$b_trial_reversal
guich_ControlCold <- (guich$'b_trial_reversal:cortControl' + guich$b_trial_reversal)
guich_CORTHot <- (guich$'b_trial_reversal:tempHot' + guich$b_trial_reversal)
guich_ControlHot <- (guich$'b_trial_reversal:cortControl:tempHot' + guich$b_trial_reversal + guich$'b_trial_reversal:cortControl' + guich$'b_trial_reversal:tempHot')
```

Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning. For _L. delicata_, hormone treatment (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B). We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L. guichenoti_ (see @fig-results C, D).

```{r, fig-results}
#| label: fig-results
#| fig.cap: "Results for L. delicata (A,B) and L. guichenoti (C, D). A, C) Predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions. The different colours represent the different treatments. B, D) Distribution of the estimates of the slopes per each treatment. The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates. The different colours represent the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
source(here("R", "func.R"))
# Create the dfs for the probability plot A and C) (df_prob)
# L. delicata
df_deliprob <- df_plotAC("deli")
# L. guichenoti
df_guichprob <- df_plotAC("guich")
#
# Create the df for the violin plots in plot B) (df_violin)
# L. delicata
df_deliV <- df_plotBD1("deli")
# L. guichenoti
df_guichV <- df_plotBD1("guich")
#
# Create the df for the points and bars in plot B) (df_points)
# L. delicata
df_deliP <- df_plotBD2("deli")
# L. guichenoti
df_guichP <- df_plotBD2("guich")
#
#
# Make plots deli and guich
source(here("R", "func.R"))
fig_deli <- plotting(sp = "deli", df_prob = df_deliprob, df_violin = df_deliV, df_points = df_deliP)
fig_guich <- plotting(sp = "guich", df_prob = df_guichprob, df_violin = df_guichV, df_points = df_guichP)
# Combine plots of both species into the final figure
fig_results <- plot_grid(fig_deli, fig_guich, ncol = 1)
ggsave("./output/figures/fig_results.png", plot=fig_results, width = 25, height = 18, units = "cm", dpi = 600)
knitr::include_graphics("./output/figures/fig_deli.png")
```

>>>>

```{r, results}
#| label: results
# Rename some of the posteriors and make means and sd for the posteriors.
## 1) L. delicata
deli_CORTCold <- deli$b_trial_reversal
deli_ControlCold <- (deli$'b_trial_reversal:cortControl' + deli$b_trial_reversal)
deli_CORTHot <- (deli$'b_trial_reversal:tempHot' + deli$b_trial_reversal)
deli_ControlHot <- (deli$'b_trial_reversal:cortControl:tempHot' + deli$b_trial_reversal + deli$'b_trial_reversal:cortControl' + deli$'b_trial_reversal:tempHot')
## 2) L. guichenoti
guich_CORTCold <- guich$b_trial_reversal
guich_ControlCold <- (guich$'b_trial_reversal:cortControl' + guich$b_trial_reversal)
guich_CORTHot <- (guich$'b_trial_reversal:tempHot' + guich$b_trial_reversal)
guich_ControlHot <- (guich$'b_trial_reversal:cortControl:tempHot' + guich$b_trial_reversal + guich$'b_trial_reversal:cortControl' + guich$'b_trial_reversal:tempHot')
```

```{r, coeficients}
#| label: coeficients
# Getting the Cohen's d coeficients of the (below) between treatments and species comparisons using the formula: 
# d =(mean1 - mean2) / sqrt((sd1^2 + sd2^2)/2)
# For the estimations of the confidence intervals we used Cohen's standard error based on the formula: se = 1 / sqrt(n1-3 + n2-3)
# And critical value:
critical_value <- qnorm((1 + 0.95) / 2)
## A) L. delicata
#### A.1.- CORT
mean_deliControl <- mean(c(deli_ControlCold, deli_ControlHot))
sd_deliControl <- sd(c(deli_ControlCold, deli_ControlHot))
mean_deliCORT <- mean(c(deli_CORTCold, deli_CORTHot))
sd_deliCORT <- sd(c(deli_CORTCold, deli_CORTHot))
#
deli_CORTd <- format_dec((mean_deliControl - mean_deliCORT) / sqrt((sd_deliControl^2 + sd_deliCORT^2)/2), 3)
#
#### A.2.- Temperature
mean_deliCold <- mean(c(deli_ControlCold, deli_CORTCold))
sd_deliCold <- sd(c(deli_ControlCold, deli_CORTCold))
mean_deliHot <- mean(c(deli_ControlHot, deli_CORTHot))
sd_deliHot <- sd(c(deli_ControlHot, deli_CORTHot))
#
deli_Tempd <- format_dec((mean_deliHot - mean_deliCold) / sqrt((sd_deliHot^2 + sd_deliCold^2)/2), 3)
#
#### A.3.- Interaction

#
## B) L. guichenoti
#### B.1.- CORT
mean_guichControl <- mean(c(guich_ControlCold, guich_ControlHot))
sd_guichControl <- sd(c(guich_ControlCold, guich_ControlHot))
mean_guichCORT <- mean(c(guich_CORTCold, guich_CORTHot))
sd_guichCORT <- sd(c(guich_CORTCold, guich_CORTHot))
#
guich_CORTd <- format_dec((mean_guichControl - mean_guichCORT) / sqrt((sd_guichControl^2 + sd_guichCORT^2)/2), 3)
#
#### B.2.- Temperature
mean_guichCold <- mean(c(guich_ControlCold, guich_CORTCold))
sd_guichCold <- sd(c(guich_ControlCold, guich_CORTCold))
mean_guichHot <- mean(c(guich_ControlHot, guich_CORTHot))
sd_guichHot <- sd(c(guich_ControlHot, guich_CORTHot))
#
guich_Tempd <- format_dec((mean_guichHot - mean_guichCold) / sqrt((sd_guichHot^2 + sd_guichCold^2)/2), 3)
#
#### B.3.- Interaction

Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning. For _L. delicata_, hormone treatment (Control - CORT = `r format_dec(mean(deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B). We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p~mcmc~ = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`, p~mcmc~ = `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L. guichenoti_ (see @fig-results C, D).

```{r, fig-results}
#| label: fig-results
#| fig.cap: "Results for L. delicata (A,B) and L. guichenoti (C, D). A, C) Predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions. The different colours represent the different treatments. B, D) Distribution of the estimates of the slopes per each treatment. The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates. The different colours represent the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
source(here("R", "func.R"))
# Create the dfs for the probability plot A and C) (df_prob)
# L. delicata
df_deliprob <- df_plotAC("deli")
# L. guichenoti
df_guichprob <- df_plotAC("guich")
#
# Create the df for the violin plots in plot B) (df_violin)
# L. delicata
df_deliV <- df_plotBD1("deli")
# L. guichenoti
df_guichV <- df_plotBD1("guich")
#
# Create the df for the points and bars in plot B) (df_points)
# L. delicata
df_deliP <- df_plotBD2("deli")
# L. guichenoti
df_guichP <- df_plotBD2("guich")
#
#
# Make plots deli and guich
source(here("R", "func.R"))
fig_deli <- plotting(sp = "deli", df_prob = df_deliprob, df_violin = df_deliV, df_points = df_deliP)
fig_guich <- plotting(sp = "guich", df_prob = df_guichprob, df_violin = df_guichV, df_points = df_guichP)
# Combine plots of both species into the final figure
fig_results <- plot_grid(fig_deli, fig_guich, ncol = 1)
ggsave("./output/figures/fig_results.png", plot=fig_results, width = 25, height = 18, units = "cm", dpi = 600)
knitr::include_graphics("./output/figures/fig_results.png")
```
